\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome5}
\usepackage{setspace}
\usepackage{parskip}

% Adjust margins
\geometry{
    top=1in,
    bottom=1in,
    left=1in,
    right=1in
}

% Remove page numbers
\pagestyle{empty}

% Set line spacing
\onehalfspacing

\begin{document}

% Header with personal information
\begin{flushleft}
\textbf{\large Your Name} \\
your.email@example.com \\
+1234567890 \\
https://linkedin.com/in/yourprofile
\end{flushleft}

\vspace{0.5in}

% Date
July 27, 2025

\vspace{0.25in}

% Recipient information
Hiring Manager \\
Sandhills Global \\

\vspace{0.25in}

% Salutation
Dear Hiring Manager,

\vspace{0.1in}

[Your Name]  
[Your Address]  
[City, State, ZIP]  
[Date]

Sandhills Global  
[Sandhills Global's Address]  
[City, State, ZIP]

I am excited to apply for the Software Development Intern position at Sandhills Global, as it presents a unique opportunity to leverage my technical expertise in a new context and contribute to the development of industry-leading software. Although my current role as a Senior Software Engineer has equipped me with a strong foundation, I am eager to dive deeper into .NET and SQL Server technologies, complementing my existing skill set that includes JavaScript, React, and a passion for innovative software solutions.

With 5 years of experience in software development, I have successfully led teams and managed projects, honing my skills in Node.js, AWS, Docker, and PostgreSQL. While my background may be rooted in Python and Node.js, my proficiency in JavaScript and React provides a solid bridge to adapt to C\textbackslash{}#, .NET, and Web APIs. A notable aspect of my approach is my ability to rapidly learn and implement new technologies, ensuring seamless integration into your development environment. For instance, in my current role, I successfully spearheaded the migration of our web application to a React.js front-end, yielding a 30\textbackslash{}% increase in user engagement.

I am particularly drawn to Sandhills Global's commitment to leveraging modern tools and technologies. I am impressed by the company's innovative approach to software development and believe my own drive for technological advancement would make me a valuable asset to your team. Through this internship, I aim not only to contribute to the company's success but also to enrich my technical portfolio with .NET and SQL Server expertise.

Thank you for considering my application. I would welcome the opportunity to discuss how my skills and experience align with the needs of the Software Development Intern role. Please feel free to contact me at [Your Phone Number] or [Your Email Address]. I look forward to the possibility of contributing to Sandhills Global's innovative software development initiatives.

[Your Name]  
Senior Software Engineer \textbackslash{}& Aspiring Software Development Intern at Sandhills Global


\vspace{0.25in}

% Closing
Sincerely,

\vspace{0.5in}

Your Name

\end{document}
