\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome5}
\usepackage{setspace}
\usepackage{parskip}

% Adjust margins
\geometry{
    top=1in,
    bottom=1in,
    left=1in,
    right=1in
}

% Remove page numbers
\pagestyle{empty}

% Set line spacing
\onehalfspacing

\begin{document}

% Header with personal information
\begin{flushleft}
\textbf{\large Roshan Scott Sanjeev} \\
roshan.sanjeev@gmail.com \\
5105095098 \\
https://www.linkedin.com/in/roshan-sanjeev/
\end{flushleft}

\vspace{0.5in}

% Date
July 27, 2025

\vspace{0.25in}

% Recipient information
Hiring Manager \\
Sandhills Global \\

\vspace{0.25in}

% Salutation
Dear Hiring Manager,

\vspace{0.1in}

Here is a compelling cover letter tailored to the provided job application:

**[Your Address]**
**[City, State, ZIP]**
**[Date]**

**Hiring Manager, Software Development Intern**
**Sandhills Global**
**[Sandhills Global's Address]**
**[City, State, ZIP]**

I am excited to apply for the Software Development Intern position at Sandhills Global, as it presents a unique opportunity to leverage my skills in a new context and contribute to the development of industry-leading software. Although my current role as a Senior Software Engineer has equipped me with a strong foundation, I am eager to dive deeper into the .NET ecosystem and expand my expertise in C\textbackslash{}#, SQL Server, and Web APIs, aligning with Sandhills Global's cutting-edge technology stack.

With a strong background in JavaScript, React, and project management, I am confident that my skills will enable me to make an immediate impact. Notably, my experience with React will facilitate a smoother transition into the company's technology environment. In my current role, I successfully led the development of a scalable web application using React, Node.js, and PostgreSQL, resulting in a 30\textbackslash{}% increase in user engagement. I am excited about the prospect of applying similar problem-solving skills to drive innovation at Sandhills Global.

I am particularly drawn to Sandhills Global's commitment to leveraging modern tools and technologies to drive software development. As someone who thrives in environments that embrace innovation, I appreciate the company's forward-thinking approach. I am eager to learn from and contribute to a team that shares my passion for software development and its transformative potential.

Thank you for considering my application. I would welcome the opportunity to discuss how my skills and experience align with the Software Development Intern role. Please feel free to contact me at **[Your Phone Number]** or **[Your Email Address]**. I look forward to the possibility of collaborating with the Sandhills Global team.

**Roshan Scott Sanjeev**


\vspace{0.25in}

% Closing
Sincerely,

\vspace{0.5in}

Roshan Scott Sanjeev

\end{document}
