\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome5}
\usepackage{setspace}
\usepackage{parskip}

% Adjust margins
\geometry{
    top=1in,
    bottom=1in,
    left=1in,
    right=1in
}

% Remove page numbers
\pagestyle{empty}

% Set line spacing
\onehalfspacing

\begin{document}

% Header with personal information
\begin{flushleft}
\textbf{\large Your Name} \\
your.email@example.com \\
+1234567890 \\
https://linkedin.com/in/yourprofile
\end{flushleft}

\vspace{0.5in}

% Date
July 27, 2025

\vspace{0.25in}

% Recipient information
Hiring Manager \\
Sandhills Global \\

\vspace{0.25in}

% Salutation
Dear Hiring Manager,

\vspace{0.1in}

[Your Name]  
[Your Address]  
[City, State ZIP Code]  
[Date]

Hiring Manager, Software Development Intern  
Sandhills Global  
[Sandhills Global's Address]  
[City, State ZIP Code]

I am excited to apply for the Software Development Intern position at Sandhills Global, as it offers a unique opportunity to leverage my technical expertise in a new context and contribute to the development of industry-leading software. Although my current role as a Senior Software Engineer has equipped me with a strong foundation, I am eager to dive deeper into the .NET ecosystem and expand my skill set in C\textbackslash{}#, SQL Server, and Web APIs, aligning with Sandhills Global's innovative technology stack.

With 5 years of experience in software development, I bring a strong background in JavaScript, React, and project management, which I believe will enable me to make an immediate impact at Sandhills Global. Notably, my proficiency in React will allow me to hit the ground running with your React.js initiatives. Furthermore, my experience with Node.js, AWS, and Docker has taught me the importance of scalable and efficient software solutions, a mindset I am excited to apply in this intern role. I am particularly drawn to this position because it embodies the perfect blend of learning and contribution, allowing for mutual growth.

One specific example of my ability to quickly adapt and deliver value is when I led a team in migrating a legacy application to a React and Node.js stack, resulting in a 40\textbackslash{}% increase in application responsiveness. I am excited about the prospect of bringing this adaptability and dedication to innovation to Sandhills Global's team. I am confident that this role will not only enhance my technical skills but also foster a deeper understanding of the industry, making me a more well-rounded professional.

Thank you for considering my application. I would welcome the opportunity to discuss how my skills and experience align with the visions of Sandhills Global. Please feel free to contact me at [Your Phone Number] or [Your Email Address]. I look forward to the possibility of contributing to and learning from your esteemed team.

[Your Name]  
Senior Software Engineer  
[Your LinkedIn Profile (Optional)]  
[Your Phone Number]  
[Your Email Address]


\vspace{0.25in}

% Closing
Sincerely,

\vspace{0.5in}

Your Name

\end{document}
